Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-02-24 docs/thesis/appendix-test_equations.tex
more diagrams: main packages, query

Eq6 & \scriptsize{Fermi Energy} & \scriptsize {\codefont <math> <msub> <mi>E</mi> <mi>F</mi> </msub> <mo>=</mo> <mfrac> <mrow> <msub> <mi>E</mi> <mi>C</mi> </msub> <mo>+</mo> <msub> <mi>E</mi> <mi>V</mi> </msub> </mrow> <mn>2</mn> </mfrac> <mo>+</mo> <mfrac> <mrow> <msub> <mi>κ</mi> <mi>B</mi> </msub> <mi>T</mi> </mrow> <mn>2</mn> </mfrac> <mi>ln</mi> <mfenced close=")" open="("> <mfrac> <msub> <mi>N</mi> <mi>V</mi> </msub> <msub> <mi>N</mi> <mi>C</mi> </msub> </mfrac> </mfenced> </math>} & \scriptsize{$E_F = \frac{E_C + E_V}{2} + \frac{\kappa_{B}T}{2} \ln \left(\frac{N_V}{N_C}\right)$ } \\ \hline

>>>>

Eq6 & \scriptsize{Dirac Equation} & \scriptsize {\codefont <math> <mfenced close=")" open="("> <mrow> <mi>β</mi> <mi>m</mi> <msup> <mi>c</mi> <mn>2</mn> </msup> <mo>+</mo> <mi>c</mi> <mfenced close=")" open="("> <mrow> <msub> <mi>α</mi> <mn>1</mn> </msub> <msub> <mi>p</mi> <mn>1</mn> </msub> <mo>+</mo> <msub> <mi>α</mi> <mn>2</mn> </msub> <msub> <mi>p</mi> <mn>2</mn> </msub> <mo>+</mo> <msub> <mi>α</mi> <mn>3</mn> </msub> <msub> <mi>p</mi> <mn>3</mn> </msub> </mrow> </mfenced> </mrow> </mfenced> <mi>ψ</mi> <mfenced close=")" open="("> <mi>x</mi> <mi>t</mi> </mfenced> <mo>==</mo> <mi>i</mi> <mi>ℏ</mi> <mfrac> <mrow> <mo>∂</mo> <mi>ψ</mi> <mfenced close=")" open="("> <mi>x</mi> <mi>t</mi> </mfenced> </mrow> <mrow> <mo>∂</mo> <mi>t</mi> </mrow> </mfrac> </math>
} & \tiny{$\left(\beta mc^2 + c(\alpha_1 p_1 +  \alpha_2 p_2 + \alpha_3 p_3)\right) \psi (x,t) = i \hbar \frac{\partial\psi(x,t) }{\partial t}$ } \\ \hline

### 2014-02-24 docs/thesis/chap-evaluation.tex
more diagrams: main packages, query

\begin{longtable}{|c|c|c|}
\hline 
Expression Length & Angular Distance Time (msec) & Tree Edit Distance Time(msec) \\ \hline 
70 & 0.01195 & 2.65  \\ \hline
145 & 0.0142 & 9.97  \\ \hline
155 & 0.0129 & 9.165  \\ \hline
185 & 0.0173 & 8.925  \\ \hline
267 & 0.0194 & 15.15  \\ \hline
405 & 0.0201 & 29.5  \\ \hline
406 & 0.0245 & 27.75  \\ \hline
442 & 0.0236 & 30.95  \\ \hline
522 & 0.0264 & 32.4  \\ \hline
719 & 0.02502 & 32.1 \\ \hline

>>>>

\begin{longtable}{|c|c|c|}
\hline 
Expression Length (Number of leaf nodes)& Angular Distance Time (msec) & Tree Edit Distance Time(msec) \\ \hline 
3 & 0.01195 & 2.65  \\ \hline
8 & 0.0142 & 9.97  \\ \hline
7 & 0.0129 & 9.165  \\ \hline
12 & 0.0194 & 15.15  \\ \hline
18 & 0.0201 & 29.5  \\ \hline
20 & 0.0245 & 27.75  \\ \hline
22 & 0.0264 & 32.4  \\ \hline
24 & 0.02502 & 32.1 \\ \hline

### 2014-02-24 docs/thesis/chap-technical_considerations.tex
more diagrams: main packages, query

\begin{longtable}{|
m{2.8cm}|>{\centering\arraybackslash}
m{2cm}|>{\centering\arraybackslash}
m{1.65cm}|>{\centering\arraybackslash}
m{1.65cm}|>{\centering\arraybackslash}
m{1.65cm}|>{\centering\arraybackslash}
m{1.95cm}|>{\centering\arraybackslash}
m{1.65cm}|>{\centering\arraybackslash}
m{1.65cm}|
}
\hline 
\textbf{Software} & \textbf{Type} & \textbf{Tested version} & \textbf{Input Format(s)} & \textbf{Output Format(s)} & \textbf{Licence Type} & \textbf{Latest Update}  \\
\hline
LaTeXML\cite{latexml} & Standalone Executable &0.7.9alpha & \LaTeX & XML + MathML & Open Source & 13 Feb 2014  \\
\hline
TeX4ht\cite{tex4ht1}\cite{tex4ht2} & Standalone Executable & 2009-01-31-07 & \LaTeX & XML + MathML & Open Source & 11 Jun 2009  \\
\hline
LaTeXmathML\cite{latexmathml} & Javascript Library & 30-October-2007 & \LaTeX & XML + MathML & Open Source & 30 Oct 2007  \\
\hline
Maxtract\cite{maxtract1}\cite{maxtract2} & Standalone Executable & v.1752 & PDF & \LaTeX / Annotated PDF & Free to download & 15 Nov 2012  \\
\hline
InftyReader\cite{infty1}\cite{infty2} & Standalone Executable (On Windows) & 2.9.6.2 & PDF, TIFF, BMP, GIF, PNG & \LaTeX, XML + MathML & Commercial & 22 Dec 2013  \\

>>>>

\begin{longtable}{|
m{2.8cm}|>{\centering\arraybackslash}
m{2cm}|>{\centering\arraybackslash}
m{1.65cm}|>{\centering\arraybackslash}
m{1.65cm}|>{\centering\arraybackslash}
m{1.65cm}|>{\centering\arraybackslash}
m{1.95cm}|>{\centering\arraybackslash}
m{1.65cm}|>{\centering\arraybackslash}
m{1.65cm}|
}
\hline 
\textbf{Software} & \textbf{Type} & \textbf{Tested version} & \textbf{Input Format(s)} & \textbf{Output Format(s)} & \textbf{Licence Type} & \textbf{Latest Update}  \\
\hline
LaTeXML\cite{latexml} & Standalone Executable &0.7.9alpha & \LaTeX & XML + MathML & Open Source & 13 Feb 2014  \\
\hline
TeX4ht\cite{tex4ht2} & Standalone Executable & 2009-01-31-07 & \LaTeX & XML + MathML & Open Source & 11 Jun 2009  \\
\hline
SnuggleTex\cite{snuggletex} & Java Library & 1.2.2 & \LaTeX (Small fragments) & MathML & Open Source & 24 May 2010  \\
\hline
LaTeXmathML\cite{latexmathml} & Javascript Library & 30-October-2007 & \LaTeX & XML + MathML & Open Source & 30 Oct 2007  \\
\hline
Maxtract\cite{maxtract1}\cite{maxtract2} & Standalone Executable & v.1752 & PDF & \LaTeX / Annotated PDF & Free to download & 15 Nov 2012  \\
\hline
InftyReader\cite{infty1}\cite{infty2} & Standalone Executable (On Windows) & 2.9.6.2 & PDF, TIFF, BMP, GIF, PNG & \LaTeX, XML + MathML & Commercial & 22 Dec 2013  \\
